\documentclass[5pt]{beamer}
\usetheme{Bergen}
\usecolortheme{seahorse}
\setbeamerfont{block title}{size=\small}
\setbeamerfont{block body}{size=\scriptsize}
\begin{document}
\begin{frame}
\frametitle{Understanding the Impact of Social Media}
\begin{columns}
\begin{column}{0.3\textwidth}
\begin{block}{\textbf{The Influence of Social Media on Everyday Life}}
Social media platforms like Facebook, Snapchat, and Twitter have become integral parts of daily routines. Many people check them first thing in the morning and last thing at night. This accessibility not only enables instant communication but also exposure to various news and events worldwide.
\end{block}
\end{column}
\begin{column}{0.3\textwidth}
\begin{block}{\textbf{Social Media's Role in Shaping Public Opinion}}
Opinions are formulated and shared in real-time through tweets and posts. Social media has emerged as a powerful tool for political campaigns, advertising, and spreading awareness on social issues. It has remarkable influence over our beliefs and attitudes.
\end{block}
\end{column}
\begin{column}{0.3\textwidth}
\begin{block}{\textbf{Addressing The Challenges and Risks Associated With Social Media}}
Despite its benefits, social media presents several issues such as privacy concerns and spread of false information. Additionally, it's addictive nature can lead to unhealthy usage patterns affecting mental health. It is essential to use these platforms responsibly and raise awareness about their potential risks.
\end{block}
\end{column}
\end{columns}
\end{frame}
\end{document}
